Local simple connectedness of boundaries of hyperbolic groups

### 2020-10-01 paper.tex
Added a discussion of proposition 6.2 to the intro
In the process, prop 6.2 becomes prop 1.3

@@

Note that the converse question has a positive answer if virtually Fuchsian
groups (which have boundary homeomorphic to a circle) are excepted:

\begin{proof}
  By Theorem~\ref{thm:main_theorem}, all point complements in $\boundary G$ are
  simply connected. Let $p$ and $q$ be distinct points in $\boundary G$. If
  $\boundary G - \set{p,q}$ is connected then $\boundary G$ is simply connected
  by the Seifert--van Kampen theorem. It follows that either $\boundary G$ is
  simply connected, or the complement of any two points in $\boundary G$ is
  disconnected, in which case $\boundary G$ is a circle
  by a classical theorem in point set topology~\cite[II.2.13]{wilder49}.
\end{proof}

>>>>

It is natural to ask whether a similar result holds in which the assumption on
the topology of point complements in $\boundary G$ is replaced by a similar
assumption on the whole of the boundary. This question is discussed in
Section~\ref{sec:conclusion}. Note however that one direction of this question
can be proved as a corollary of Theorem~\ref{thm:main_theorem}, at least when
circular boundaries (for which the implication does not hold) are excepted.

@@

Note that the converse question has a positive answer if virtually Fuchsian
groups (which have boundary homeomorphic to a circle) are excepted. This is the
content of Proposition~\ref{prop:converse_theorem}, which we now prove.

\begin{proof}[Proof of Proposition~\ref{prop:converse_theorem}]
  By Theorem~\ref{thm:main_theorem}, all point complements in $\boundary G$ are
  simply connected. Let $p$ and $q$ be distinct points in $\boundary G$. If
  $\boundary G - \set{p,q}$ is connected then $\boundary G$ is simply connected
  by the Seifert--van Kampen theorem. It follows that either $\boundary G$ is
  simply connected, or the complement of any two points in $\boundary G$ is
  disconnected, in which case $\boundary G$ is a circle
  by a classical theorem in point set topology~\cite[II.2.13]{wilder49}.
\end{proof}
